\chapter*{Summary}
This research project focused on designing, implementing and testing a multiplayer online game (MOG) using Named Data Networking (NDN) as the primary communication mechanism. A literature review was conducted resulting in a detailed overview of the current state of the art in the fields of NDN and MOG networking. Modern MOGs were also examined in order to develop a taxonomy of the data generated in MOGs. Each of the categories identified by the taxonomy have different characteristics and require different networking solutions to provide a consistent view of the game world to all players. 

The results of this research led to the design and implementation of a 2D MOG in order to facilitate the testing and evaluation of an NDN based backend for the game. The game allows players to move around a virtual game world, shoot projectiles at other players and to place blocks which can be used as cover. These game mechanics were chosen as they provide a good coverage of the categories of data identified by the taxonomy. 

A P2P NDN based backend was developed for the game which uses existing NDN software, as well as a novel protocol for synchronizing remote game objects over NDN, to provide a high-performance networking solution required by a fast paced MOG.

A system for automating game players was created to facilitate the testing of the game. This was done by creating a Docker container for an automated player and deploying these containers onto an Amazon Web Services cluster using a Docker swarm.  

Finally, the performance of the game was evaluated under a variety of network topologies and scenarios by analysing the data produced during the testing period. The results showed that the features of NDN such as interest aggregation and native multicast enabled the game easily support 16 concurrent players. Several networking optimizations were also developed to further reduce the network traffic generated by the game, further increasing scalability.